Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions

### 2024-01-17 paper/arxiv/supp_3_ml.tex
continue clean up tables
clean up table formats

% Supplementary Table 15: Notations for elementary descriptors and electronic descriptors
\begin{table}[htbp]
  \centering
  \begin{tabular}{lp{5cm}lp{5cm}}
    \toprule
    \multicolumn{2}{c}{Elementary Descriptors}       & \multicolumn{2}{c}{Electronic Descriptors}            \\
    \midrule
    $R$            & atomic radius                   & $\alpha$, $\beta$, $\gamma$  & lattice parameters     \\
    $E_\text{ea}$  & electron affinity               & $\Phi_{\text{DFT}}$    & DFT calculated work function \\
    $\Phi$         & work function                   & $E_\text{vac}$         & vacuum level                 \\
    $\chi_\text{Allen}$, $\chi_\text{P}$, $\chi_\text{RevP}$
    & \parbox[t]{4cm}{electronegativity in Allen, Pauling and revised Pauling scales}
    & $E_\text{g}$, $E_\text{g}\uparrow$, $E_\text{g}\uparrow$
    & \parbox[t]{4cm}{average, spin-up and spin-down band gaps}                                              \\
    $A_\text{r}$   & relative atomic mass            & $e_\text{d}$           & number of d-electrons        \\
    $E_\text{i}$   & ionization energy & $\delta\epsilon_{\text{d}}\uparrow$  & d-band centre (spin-up)      \\
    $G$            & group number                    & $W_\text{d}$           & d-band width                 \\
    $P$            & period number                   & $e_{\text{Bader}}$     & Bader charge                 \\
    $V$            & number of valence electrons     &                        &                              \\
    \bottomrule
  \end{tabular}
  \caption{Notations for elementary descriptors and electronic descriptors}
  \label{supp_table15:descriptor_notations}
\end{table}

@@

% Supplementary Table 16: The hyperparameter search space
\begin{table}[htbp]
  \centering
  \begin{tabular}{llp{5cm}}
    \toprule
    Hyperparameter& Search Space              & Description                                                       \\
    \midrule
    learningRate  & [10\textsuperscript{-4}, 10\textsuperscript{-2}], log scale & Learning rate of Adam \cite{kingma2017adam} optimizer \\
    dropoutRate   & [0, 1]                    & Dropout rate                                                      \\
    root\_fc0     & 128, 256, 512             & Output dimensionality of 1\textsuperscript{st} fully connected layer in root           \\
    root\_fc1     & 256, 512, 1024, 2048      & Output dimensionality of 2\textsuperscript{nd} fully connected layer in root           \\
    root\_act     & ``tanh'', ``relu'', ``sigmoid'' & Activation function of fully connected layers in root             \\
    kernelSize    & [2, 32]                   & Width of the convolution window                                   \\
    numFilters    & [8, 64]                   & Number of filters in the convolution                              \\
    numConvLayers & [1, 16]                   & Number of convolution layers                                      \\
    numConvBlocks & [1, 16]                   & Number of convolution blocks                                      \\
    br\_fc0       & 16, 32, 64, 128, 256, 512 & Output dimensionality of 1\textsuperscript{st} fully connected layer in branch      \\
    br\_fc1       & 8, 16, 32, 64, 128, 256   & Output dimensionality of 2\textsuperscript{nd} fully connected layer in branch      \\
    br\_act       & ``tanh'', ``relu'', ``sigmoid'' & Activation function of fully connected layers in branch           \\
    \bottomrule
  \end{tabular}
  \caption{The hyperparameter search space}
  \label{supp_table16:hyperparam_space}
\end{table}

% Supplementary Table 17: Optimal hyperparameters identified with Hyperband algorithm
\begin{table}[htbp]
  \centering
  \begin{tabular}{llp{6cm}}
    \toprule
    Hyperparameter& Optimal Value & Description                                              \\
    \midrule
    learningRate  & $10^{-3}$ & Learning rate of Adam \cite{kingma2017adam} optimizer                              \\
    dropoutRate   & 0.3       & Dropout rate                                                 \\
    root\_fc0     & 256       & Output dimensionality of 1\textsuperscript{st} fully connected layer in root   \\
    root\_fc1     & 512       & Output dimensionality of 2\textsuperscript{nd} fully connected layer in root   \\
    root\_act     & ``relu''    & Activation function of fully connected layers in root        \\
    kernelSize    & 10        & Width of convolution window                                  \\
    numFilters    & 17        & Number of filters in the convolution                         \\
    numConvLayers & 3         & Number of convolution layers                                 \\
    numConvBlocks & 1         & Number of convolution blocks                                 \\
    br\_fc0       & 256       & Output dimensionality of 1\textsuperscript{st} fully connected layer in branch \\
    br\_fc1       & 128       & Output dimensionality of 2\textsuperscript{nd} fully connected layer in branch \\
    br\_act       & ``tanh''    & Activation function of fully connected layers in branch      \\
    \bottomrule
  \end{tabular}
  \caption{Optimal hyperparameters identified with Hyperband algorithm}
  \label{supp_table17:opt_hyperparam}
\end{table}

% Supplementary Table 18: Prediction MAEs of the CNN model
\begin{table}[htbp]
  \centering
  \begin{tabular}{lll}
    \toprule
    Adsorbate             & Original dataset (eV)  & Augmented dataset (eV)  \\
    \midrule
    CO\textsubscript{2}   & 0.0447                 & 0.0336                  \\
    COOH                  & 0.0436                 & 0.0581                  \\
    CO                    & 0.0402                 & 0.0402                  \\
    CHO                   & 0.0614                 & 0.0778                  \\
    CH\textsubscript{2}O  & 0.0553                 & 0.0632                  \\
    OCH\textsubscript{3}  & 0.0605                 & 0.0636                  \\
    O                     & 0.1135                 & 0.1081                  \\
    OH                    & 0.0547                 & 0.0602                  \\
    H                     & 0.0703                 & 0.0646                  \\
    \bottomrule
  \end{tabular}
  \caption{Prediction mean absolute errors of the CNN model}
  \tablefootnote{The same CNN model, trained on the augmented dataset, was used for all predictions.
  The term ``original dataset'' refers to evaluations conducted on the original dataset without any augmented data;
  it does not imply the use of a different CNN model trained solely on the original dataset.
  Similarly, ``augmented dataset'' refers to evaluations on the dataset with both original data and augment data,
  not a distinct model.}
  \label{supp_table18:cnn_mae}
\end{table}

>>>>

% Supplementary Table 15: Notations for elementary descriptors and electronic descriptors
\begin{table}[htbp]
\label{supp_table15:descriptor_notations}
  \caption{Notations for elementary descriptors and electronic descriptors}
  \small
  \begin{tabularx}{\textwidth}{@{}llll@{}}
    \toprule
    \multicolumn{2}{c}{Elementary Descriptors}       & \multicolumn{2}{c}{Electronic Descriptors}            \\
    \midrule
    $R$            & atomic radius                   & $\alpha$, $\beta$, $\gamma$  & lattice parameters     \\
    $E_\text{ea}$  & electron affinity               & $\Phi_{\text{DFT}}$    & DFT calculated work function \\
    $\Phi$         & work function                   & $E_\text{vac}$         & vacuum level                 \\
    $\chi_\text{Allen}$, $\chi_\text{P}$, $\chi_\text{RevP}$
    & \parbox[t]{4cm}{electronegativity in Allen, Pauling and revised Pauling scales}
    & $E_\text{g}$, $E_\text{g}\uparrow$, $E_\text{g}\uparrow$
    & \parbox[t]{4cm}{average, spin-up and spin-down band gaps}                                              \\
    $A_\text{r}$   & relative atomic mass            & $e_\text{d}$           & number of d-electrons        \\
    $E_\text{i}$   & ionization energy & $\delta\epsilon_{\text{d}}\uparrow$  & d-band centre (spin-up)      \\
    $G$            & group number                    & $W_\text{d}$           & d-band width                 \\
    $P$            & period number                   & $e_{\text{Bader}}$     & Bader charge                 \\
    $V$            & number of valence electrons     &                        &                              \\
    \bottomrule
  \end{tabularx}
\end{table}

@@

% Supplementary Table 16: The hyperparameter search space
\begin{table}[htbp]
\label{supp_table16:hyperparam_space}
  \caption{The hyperparameter search space}
  \small
  \begin{tabularx}{\textwidth}{@{}lXX@{}}
    \toprule
    Hyperparameter& Search Space              & Description                                                       \\
    \midrule
    learningRate  & [10\textsuperscript{-4}, 10\textsuperscript{-2}], log scale & Learning rate of Adam \cite{kingma2017adam} optimizer \\
    dropoutRate   & [0, 1]                    & Dropout rate                                                      \\
    root\_fc0     & 128, 256, 512             & Output dimensionality of 1\textsuperscript{st} fully connected layer in root           \\
    root\_fc1     & 256, 512, 1024, 2048      & Output dimensionality of 2\textsuperscript{nd} fully connected layer in root           \\
    root\_act     & ``tanh'', ``relu'', ``sigmoid'' & Activation function of fully connected layers in root             \\
    kernelSize    & [2, 32]                   & Width of the convolution window                                   \\
    numFilters    & [8, 64]                   & Number of filters in the convolution                              \\
    numConvLayers & [1, 16]                   & Number of convolution layers                                      \\
    numConvBlocks & [1, 16]                   & Number of convolution blocks                                      \\
    br\_fc0       & 16, 32, 64, 128, 256, 512 & Output dimensionality of 1\textsuperscript{st} fully connected layer in branch      \\
    br\_fc1       & 8, 16, 32, 64, 128, 256   & Output dimensionality of 2\textsuperscript{nd} fully connected layer in branch      \\
    br\_act       & ``tanh'', ``relu'', ``sigmoid'' & Activation function of fully connected layers in branch           \\
    \bottomrule
  \end{tabularx}
\end{table}

% Supplementary Table 17: Optimal hyperparameters identified with Hyperband algorithm
\begin{table}[htbp]
\label{supp_table17:opt_hyperparam}
  \caption{Optimal hyperparameters identified with Hyperband algorithm}
  \small
  \begin{tabularx}{\textwidth}{@{}lXX@{}}
    \toprule
    Hyperparameter& Optimal Value & Description                                              \\
    \midrule
    learningRate  & $10^{-3}$ & Learning rate of Adam \cite{kingma2017adam} optimizer                              \\
    dropoutRate   & 0.3       & Dropout rate                                                 \\
    root\_fc0     & 256       & Output dimensionality of 1\textsuperscript{st} fully connected layer in root   \\
    root\_fc1     & 512       & Output dimensionality of 2\textsuperscript{nd} fully connected layer in root   \\
    root\_act     & ``relu''    & Activation function of fully connected layers in root        \\
    kernelSize    & 10        & Width of convolution window                                  \\
    numFilters    & 17        & Number of filters in the convolution                         \\
    numConvLayers & 3         & Number of convolution layers                                 \\
    numConvBlocks & 1         & Number of convolution blocks                                 \\
    br\_fc0       & 256       & Output dimensionality of 1\textsuperscript{st} fully connected layer in branch \\
    br\_fc1       & 128       & Output dimensionality of 2\textsuperscript{nd} fully connected layer in branch \\
    br\_act       & ``tanh''    & Activation function of fully connected layers in branch      \\
    \bottomrule
  \end{tabularx}
\end{table}

% Supplementary Table 18: Prediction MAEs of the CNN model
\begin{table}[htbp]
\label{supp_table18:cnn_mae}
  \caption{Prediction mean absolute errors of the CNN model}
  \small
  \begin{tabularx}{\textwidth}{@{}lXX@{}}
    \toprule
    Adsorbate             & Original dataset (eV)  & Augmented dataset (eV)  \\
    \midrule
    CO\textsubscript{2}   & 0.0447                 & 0.0336                  \\
    COOH                  & 0.0436                 & 0.0581                  \\
    CO                    & 0.0402                 & 0.0402                  \\
    CHO                   & 0.0614                 & 0.0778                  \\
    CH\textsubscript{2}O  & 0.0553                 & 0.0632                  \\
    OCH\textsubscript{3}  & 0.0605                 & 0.0636                  \\
    O                     & 0.1135                 & 0.1081                  \\
    OH                    & 0.0547                 & 0.0602                  \\
    H                     & 0.0703                 & 0.0646                  \\
    \bottomrule
  \end{tabularx}
  \bigskip
  \small\textit{Note:} The same CNN model, trained on the
    augmented dataset, was used for all predictions. The term ``original dataset''
    refers to evaluations conducted on the original dataset without any augmented data;
    it does not imply the use of a different CNN model trained solely on the original dataset.
    Similarly, ``augmented dataset'' refers to evaluations on the dataset with
    both original data and augment data, not a distinct model.
\end{table}

### 2024-01-17 paper/arxiv/supp_4_others.tex
continue clean up tables
clean up table formats

The hyperparameter optimization for the proposed CNN model was performed using NVIDIA\textsuperscript{\textregistered} V100 Tensor Core GPUs,
courtesy of the Australian National Computational Infrastructure's (NCI) HPC Gadi system.
The HyperBand algorithm \cite{li2018hyperband}, as implemented in KerasTuner \cite{omalley2019kerastuner} , facilitated the tuning process.

% Supplementary Table 19: Packages in the DL env
\begin{table}[htbp]
  \centering
  \begin{tabular}{llll}
    \toprule
    Name                & Version & Build                        & Channel     \\
    \midrule
    conda               & 4.13.0  & py39h06a4308\textunderscore0 & anaconda    \\
    cuda-nvcc           & 11.8.89 & 0                            & nvidia      \\
    cuda-toolkit        & 11.8.0  & 0                            & nvidia      \\
    cudatoolkit         & 11.6.0  & habf752d\textunderscore9     & nvidia      \\
    ipykernel           & 6.9.1   & py39h06a4308\textunderscore0 & anaconda    \\
    ipython             & 7.34.0  & pypi\textunderscore0         & pypi        \\
    jupyter\_client     & 7.2.2   & py39h06a4308\textunderscore0 & anaconda    \\
    jupyterlab          & 3.4.4   & py39h06a4308\textunderscore0 & anaconda    \\
    keras               & 2.9.0   & pypi\textunderscore0         & pypi        \\
    keras-preprocessing & 1.1.2   & pypi\textunderscore0         & pypi        \\
    keras-tuner         & 1.3.5   &                              & pypi        \\
    matplotlib          & 3.5.1   & py39h06a4308\textunderscore1 & anaconda    \\
    numpy               & 1.22.4  & pypi\textunderscore0         & pypi        \\
    pandas              & 1.3.4   & py39h8c16a72\textunderscore0 & anaconda    \\
    python              & 3.9.12  & h12debd9\textunderscore1     & anaconda    \\
    scikit-learn        & 1.1.1   & py39h6a678d5\textunderscore0 & anaconda    \\
    scipy               & 1.8.1   & py39hddc5342\textunderscore3 & conda-forge \\
    tensorboard         & 2.9.1   & pypi\textunderscore0         & pypi        \\
    tensorflow          & 2.9.3   & pypi\textunderscore0         & pypi        \\
    tensorflow-gpu      & 2.9.3   & pypi\textunderscore0         & pypi        \\
    xlrd                & 2.0.1   & pyhd3eb1b0\textunderscore0   & anaconda    \\
    yaml                & 0.2.5   & h7b6447c\textunderscore0     & anaconda    \\
    \bottomrule
  \end{tabular}
  \caption{Core packages in the deep learning environment}
  \tablefootnote{The complete list of packages is provided along with the source code.}
  \label{supp_table19:pack_dl_env}
\end{table}

@@

% Supplementary Table 20: Packages in data analysis and vis env
\begin{table}[htbp]
  \centering
  \begin{tabular}{llll}
    \toprule
    Name             & Version & Build                    & Channel \\
    \midrule
    bokeh            & 3.2.2   & pypi\textunderscore0     & pypi    \\
    colorcet         & 3.0.1   & pypi\textunderscore0     & pypi    \\
    heatmapz         & 0.0.4   & pypi\textunderscore0     & pypi    \\
    keras            & 2.13.1  & pypi\textunderscore0     & pypi    \\
    keras-tuner      & 1.3.5   & pypi\textunderscore0     & pypi    \\
    matplotlib       & 3.7.2   & pypi\textunderscore0     & pypi    \\
    numpy            & 1.24.3  & pypi\textunderscore0     & pypi    \\
    pandas           & 2.0.3   & pypi\textunderscore0     & pypi    \\
    python           & 3.11.4  & hb885b13\textunderscore0 &         \\
    pyyaml           & 6.0.1   & pypi\textunderscore0     & pypi    \\
    scikit-learn     & 1.3.0   & pypi\textunderscore0     & pypi    \\
    scipy            & 1.11.1  & pypi\textunderscore0     & pypi    \\
    seaborn          & 0.12.2  & pypi\textunderscore0     & pypi    \\
    tensorboard      & 2.13.0  & pypi\textunderscore0     & pypi    \\
    tensorflow       & 2.13.0  & pypi\textunderscore0     & pypi    \\
    tensorflow-macos & 2.13.0  & pypi\textunderscore0     & pypi    \\
    \bottomrule
  \end{tabular}
  \caption{Core packages in data analysis and visualization environment}
  \tablefootnote{The complete list of packages is provided along with the source code.}
  \label{supp_table20:pack_vis_env}
\end{table}

>>>>

The hyperparameter optimization for the proposed CNN model was performed using NVIDIA\textsuperscript{\textregistered} V100 Tensor Core GPUs,
courtesy of the Australian National Computational Infrastructure's (NCI) HPC Gadi system.
The HyperBand algorithm \cite{li2018hyperband}, as implemented in
KerasTuner \cite{omalley2019kerastuner}, facilitated the tuning process.

% Supplementary Table 19: Packages in the DL env
\begin{table}[htbp]
\label{supp_table19:pack_dl_env}
  \caption{Core packages in the deep learning environment}
  \small
  \begin{tabularx}{\textwidth}{@{}l *{3}{X} @{}}
    \toprule
    Name                 & Version  & Build                         & Channel      \\
    \midrule
    conda                & 4.13.0   & py39h06a4308\textunderscore0  & anaconda     \\
    cuda-nvcc            & 11.8.89  & 0                             & nvidia       \\
    cuda-toolkit         & 11.8.0   & 0                             & nvidia       \\
    cudatoolkit          & 11.6.0   & habf752d\textunderscore9      & nvidia       \\
    ipykernel            & 6.9.1    & py39h06a4308\textunderscore0  & anaconda     \\
    ipython              & 7.34.0   & pypi\textunderscore0          & pypi         \\
    jupyter\_client      & 7.2.2    & py39h06a4308\textunderscore0  & anaconda     \\
    jupyterlab           & 3.4.4    & py39h06a4308\textunderscore0  & anaconda     \\
    keras                & 2.9.0    & pypi\textunderscore0          & pypi         \\
    keras-preprocessing  & 1.1.2    & pypi\textunderscore0          & pypi         \\
    keras-tuner          & 1.3.5    &                               & pypi         \\
    matplotlib           & 3.5.1    & py39h06a4308\textunderscore1  & anaconda     \\
    numpy                & 1.22.4   & pypi\textunderscore0          & pypi         \\
    pandas               & 1.3.4    & py39h8c16a72\textunderscore0  & anaconda     \\
    python               & 3.9.12   & h12debd9\textunderscore1      & anaconda     \\
    scikit-learn         & 1.1.1    & py39h6a678d5\textunderscore0  & anaconda     \\
    scipy                & 1.8.1    & py39hddc5342\textunderscore3  & conda-forge  \\
    tensorboard          & 2.9.1    & pypi\textunderscore0          & pypi         \\
    tensorflow           & 2.9.3    & pypi\textunderscore0          & pypi         \\
    tensorflow-gpu       & 2.9.3    & pypi\textunderscore0          & pypi         \\
    xlrd                 & 2.0.1    & pyhd3eb1b0\textunderscore0    & anaconda     \\
    yaml                 & 0.2.5    & h7b6447c\textunderscore0      & anaconda     \\
    \bottomrule
  \end{tabularx}
  \bigskip
  \small\textit{Note:} The complete list of packages is
    provided along with the source code
\end{table}

@@

% Supplementary Table 20: Packages in data analysis and vis env
\begin{table}[htbp]
\label{supp_table20:pack_vis_env}
  \caption{Core packages in data analysis and visualization environment}
  \small
  \begin{tabularx}{\textwidth}{@{}l *{3}{X} @{}}
    \toprule
    Name              & Version  & Build                     & Channel  \\
    \midrule
    bokeh             & 3.2.2    & pypi\textunderscore0      & pypi     \\
    colorcet          & 3.0.1    & pypi\textunderscore0      & pypi     \\
    heatmapz          & 0.0.4    & pypi\textunderscore0      & pypi     \\
    keras             & 2.13.1   & pypi\textunderscore0      & pypi     \\
    keras-tuner       & 1.3.5    & pypi\textunderscore0      & pypi     \\
    matplotlib        & 3.7.2    & pypi\textunderscore0      & pypi     \\
    numpy             & 1.24.3   & pypi\textunderscore0      & pypi     \\
    pandas            & 2.0.3    & pypi\textunderscore0      & pypi     \\
    python            & 3.11.4   & hb885b13\textunderscore0  &          \\
    pyyaml            & 6.0.1    & pypi\textunderscore0      & pypi     \\
    scikit-learn      & 1.3.0    & pypi\textunderscore0      & pypi     \\
    scipy             & 1.11.1   & pypi\textunderscore0      & pypi     \\
    seaborn           & 0.12.2   & pypi\textunderscore0      & pypi     \\
    tensorboard       & 2.13.0   & pypi\textunderscore0      & pypi     \\
    tensorflow        & 2.13.0   & pypi\textunderscore0      & pypi     \\
    tensorflow-macos  & 2.13.0   & pypi\textunderscore0      & pypi     \\
    \bottomrule
  \end{tabularx}
  \bigskip
  \small\textit{Note:} The complete list of packages
    is provided along with the source code.
\end{table}
